### 2015-03-04 paper_40_cri.tex
working on case study - quality
updated case study availability

                \begin{displaymath}
                   S_{1_i} = \left\{
                     \begin{array}{lr}
                       \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \times k  \\
                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{6\sigma_i} \times k
                     \end{array}
                   \right] \text{   , calculate quality score for each app $i$}
                \end{displaymath} 
                where
                \begin{itemize}
                    \item $S_{1_i}$ is the quality score for Application ID $i$
                    \item $n$ is the number of Application IDs
                    \item $d_i$ is the actual PROD defects
                    \item $f_i$ is the function to predict PROD defects for Application $i$ based upon 
                        \textit{UAT Defects}, \textit{SIT Defects}, \textit{Testing Effort}, 
                        and \textit{Development Effort}
                    \item $6\sigma$ 6 times an estimate of the standard deviation of the 
                        population using function $f_i$ above
                \end{itemize}

@@

    \subsection{CRI COMPARED}

>>>>

                \begin{displaymath}
                   S_{1_i} = \left\{
                     \begin{array}{lr}
                       \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \times k  \\
                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{6\sigma_i} \times k
                     \end{array}
                   \right] \text{   , calculate quality score for each app $i$}
                \end{displaymath} 
                where
                \begin{itemize}
                    \item $S_{1_i}$ is the quality score for Application ID $i$
                    \item $n$ is the number of Application IDs
                    \item $d_i$ is the actual PROD defects
                    \item $f_i$ is the function to predict PROD defects for Application $i$ based upon 
                        \textit{UAT Defects}, \textit{SIT Defects}, \textit{Testing Effort}, 
                        and \textit{Development Effort}
                    \item $\sigma^2$ is the estimated variance
                \end{itemize}

@@

    \subsection{CRI COMPARED}
        CRI is one way to evaluate an SDO, and it is also a technique of
        software analytics.  Therefore, it is beneficial to compare CRI
        with some of the other techniques and guidelines available. The
        next sections will provide those comparisons.

### 2015-03-04 paper_70_case-study.tex
finishing quality for case study
updated case study availability

    \subsection{WITH HISTORICAL DATA}
        After the data has been collected, the raw data can be stored in the SDLC
        if desired.  Then scores for each of the 4 elements can be calculated.
        For this example, the value of $k$ will be 100 and the time
        frequency will be monthly.  Thus, scores will fall
        in the range $[-100,100]$.
        \subsubsection{QUALITY}
            The first step to dealing with the quality data is a quick
            analysis of the data.  Table \ref{tab:quality_desc} provides
            some descriptive statistics for the quality data.  Testing hours
            were not capture but they are optional, so the analysis can 
            continue.

@@

            Now that $f$ has been determined, the quality scores for each
            application can be calculated for all the months beyond 2013.

        \subsubsection{AVAILABILITY}
        \subsubsection{SCHEDULE}
        \subsubsection{REQUIREMENTS}
        \subsubsection{OVERALL}
            All of the months do not include the same elements.

>>>>

    \subsection{WITH HISTORICAL DATA}
        After the data has been collected, the raw data can be stored in the SDLC
        if desired.  Then scores for each of the 4 elements can be calculated.
        For this example, the value of $k$ will be 100 and the time
        frequency will be monthly.  Thus, scores will fall
        in the range $[-100,100]$.  Also, equal weighting is applied to 
        all elements and all Project IDs, Application IDs, and System IDs.
        \subsubsection{QUALITY}
            The first step to dealing with the quality data is a quick
            analysis of the data.  Table \ref{tab:quality_desc} provides
            some descriptive statistics for the quality data.  Testing hours
            were not capture but they are optional, so the analysis can 
            continue.

@@

            Now that $f$ has been determined, the quality scores for each
            application can be calculated for all the months beyond 2013.
            Appendix \ref{src:quality} provides the necessary R code to
            perform the calculations.  Figure \ref{fig:quality-scores} shows
            the quality scores for 2014 and beyond.  As can be seen, the
            scores are greatly above expectations.  That is an indication
            of improved quality over historical performance.

            \begin{figure}[ht]
                \centering
                \includegraphics[scale=.3]{images/quality_scores.png}
                \caption{CRI QUALITY SCORES}
                \label{fig:quality-scores}
            \end{figure}

        \subsubsection{AVAILABILITY}
            For the availability data,
            some descriptive statistics can be seen in 
            Table \ref{tab:availability_desc}.  The percent uptime
            was precalculated for this data so uptime, scheduled downtime,
            and unscheduled downtime are not needed.  Availability
            does not rely upon analysis of historical data since
            a known upper and lower bound exist, 1 and 0 respectively.

                Percent Uptime & 0 & 1.0 & 1.0 & 0.9745 & 0.023 \\
                \myrowcolour%
                Expected Percent Uptime & 0.93 & 1.0 & 0.98 & 0.9769  & 0.977\\

                \multicolumn{6}{c}{7522 obs. from 83 Application IDs from 2008 to 2015} \\

                \caption{AVAILABILITY DATA DESCRIPTIVE STATISTICS}
                \label{tab:availability_desc}
            \end{longtable}

            Since percent uptime has already been calculated and no historical
            analysis needs to be performed, the calculation of the scores
            can be performed. 
            R code to compute the CRI availability scores can be found in Appendix
            \ref{src:availability}. Figure \ref{fig:availability-scores} displays
            the CRI availability scores.  As can be seen the scores are all above
            70.  That is good from a performance standpoint, but it might be an
            indication that the expected uptimes could be raised.  If expected
            uptimes are consistently being exceeded, some consideration should
            be given to increase the expected uptimes.  This shows that
            organizations, or at least this particular organization, are getting
            very good at keeping computer systems available.  Therefore,
            SLAs need to be adjusted to properly reflect the better performance.

            \begin{figure}[ht]
                \centering
                \includegraphics[scale=.3]{images/availability_scores.png}
                \caption{CRI AVAILABILITY SCORES}
                \label{fig:availability-scores}
            \end{figure}

        \subsubsection{SCHEDULE}
        \subsubsection{REQUIREMENTS}
        \subsubsection{OVERALL}
            All of the months do not include the same elements.
